---
title: "Exelixis Dummy Data QA Report"
subtitle: "SDTM and ADaM Datasets"
author: "Brian Carter"
date: today
format:
  html:
    toc: true
    toc-depth: 3
    toc-location: left
    number-sections: true
    code-fold: true
    theme: cosmo
    embed-resources: true
---

```{r setup}
#| echo: false
#| warning: false
#| message: false

library(haven)
library(dplyr)
library(knitr)
library(stringr)
library(here)

# Source summary functions
source(here("R/summarize_numeric.R"))
source(here("R/summarize_character.R"))
source(here("R/summarize_date.R"))
source(here("R/summarize_variable.R"))
source(here("R/extract_dataset_metadata.R"))

# Load all SDTM datasets from data directory
sdtm_dir <- here("projects/exelixis-sap/output-data/sdtm")
sdtm_files <- list.files(sdtm_dir, pattern = "^[a-z]{2}\\.xpt$", full.names = TRUE)

# Read all SDTM datasets
sdtm_datasets <- list()
for (file in sdtm_files) {
  domain <- toupper(tools::file_path_sans_ext(basename(file)))
  sdtm_datasets[[domain]] <- read_xpt(file)
}

# Load all ADaM datasets from output-data/adam directory
adam_dir <- here("projects/exelixis-sap/output-data/adam")
adam_files <- list.files(adam_dir, pattern = "^ad[a-z]+\\.rds$", full.names = TRUE)

# Read all ADaM datasets
adam_datasets <- list()
for (file in adam_files) {
  domain <- toupper(tools::file_path_sans_ext(basename(file)))
  adam_datasets[[domain]] <- readRDS(file)
}
```

# Overview {.unnumbered}

This report provides quality assurance summaries for all SDTM and ADaM datasets in the Exelixis SAP project.

::: {.callout-important}
## Data Quality Notice

**These datasets were AI-generated and should be considered a first pass at this process.** All data must be validated before use. Part of the validation process is reviewing this QA output to identify issues, inconsistencies, and missing values.
:::

**Report Generated:** `r format(Sys.Date(), "%Y-%m-%d")`

**SDTM Domains:** `r length(sdtm_datasets)` (`r paste(names(sdtm_datasets), collapse = ", ")`)

**ADaM Datasets:** `r length(adam_datasets)` (`r paste(names(adam_datasets), collapse = ", ")`)

---

# SDTM Domains

```{r}
#| echo: false
#| results: asis

# Process each SDTM domain
for (domain in names(sdtm_datasets)) {
  dataset <- sdtm_datasets[[domain]]

  # Create domain section header
  cat("\n\n## ", domain, " Dataset\n\n", sep = "")
  cat("**Total Records:** ", nrow(dataset), "\n\n", sep = "")
  cat("**Total Variables:** ", ncol(dataset), "\n\n", sep = "")

  # Extract and display dataset metadata
  metadata <- extract_dataset_metadata(dataset)
  print(kable(metadata, align = c("l", "l", "r", "l", "l")))
  cat("\n\n")

  # Get all variable names
  var_names <- names(dataset)

  # Process each variable
  for (var in var_names) {
    # Create subsection for this variable (just variable name)
    cat("\n\n### ", var, "\n\n", sep = "")

    # Get variable data
    var_data <- dataset[[var]]

    # Generate summary based on variable type
    summary_result <- summarize_variable(var_data, var)

    # Display as table
    print(kable(summary_result))
    cat("\n\n")
  }
}
```

---

# ADaM Datasets

```{r}
#| echo: false
#| results: asis

# Process each ADaM dataset
for (domain in names(adam_datasets)) {
  dataset <- adam_datasets[[domain]]

  # Create dataset section header
  cat("\n\n## ", domain, " Dataset\n\n", sep = "")
  cat("**Total Records:** ", nrow(dataset), "\n\n", sep = "")
  cat("**Total Variables:** ", ncol(dataset), "\n\n", sep = "")

  # Extract and display dataset metadata
  metadata <- extract_dataset_metadata(dataset)
  print(kable(metadata, align = c("l", "l", "r", "l", "l")))
  cat("\n\n")

  # Get all variable names
  var_names <- names(dataset)

  # Process each variable
  for (var in var_names) {
    # Create subsection for this variable (just variable name)
    cat("\n\n### ", var, "\n\n", sep = "")

    # Get variable data
    var_data <- dataset[[var]]

    # Generate summary based on variable type
    summary_result <- summarize_variable(var_data, var)

    # Display as table
    print(kable(summary_result))
    cat("\n\n")
  }
}
```

---

::: {.callout-note}
## Report Information

**Prepared by:** Brian Carter

**Date:** `r format(Sys.Date(), "%Y-%m-%d")`

**Purpose:** Quality assurance review of SDTM and ADaM datasets for the Exelixis SAP project. This report summarizes all variables across all domains and datasets to identify data quality issues, missing values, and distribution patterns.
:::
